%\documentclass{UUThesisTemplate}
%\begin{document}
\chapter*{Acknowledgements}%
First and foremost, I am very grateful to my main advisor Joakim Nivre, who has taken an active interest in my work. I am grateful for his patience and his immense knowledge of natural language processing which, taken together, make him a brilliant mentor. 
 I am also grateful to my assistant advisors, Marcel Cori and Mats Dahllöf, for their thoughtful guidance.
 
Special thanks are due to my current and former colleagues in the computational linguistics group for their support, scholarly interaction, kind messages, and company throughout the years. Special acknowledgements go to Fabienne Cap, Christian Hardmeier, Sara Stymne, Aaron Smith, Miryam de Lhoneux, Beáta Megyesi, Gongbo Tang, Yan Shao, Ali Basirat, Eva Pettersson, Nils Blomqvist, Mojgan Seraji, Oscar Täckström, and Mattias Nilsson. 

My gratitude also goes to all the other members of the department for sharing meals, coffees, choir sessions or simply a good discussion. I would especially like to thank: Heinz Werner Wessler, Christer Henriksén, Karin Koltay, Eric Cullhed, Michael Dunn, Jakob Andersson, Helena Löthman, Johan Heldt, Christian Schaefer, and Harald Hammarström.  

I also address my deep thanks and encouragement to all the other PhD fellows at the department, namely Rima Haddad, Josefin Lindgren, Alexander Nilsson, Marc Tang,  Linnéa Öberg, Vera Wilhelmsen, Jaroslava Obrtelova, Fredrik Sixtensson, Myrto Veikou, Emil Lundin, Samuel Douglas, Mahmut Agbaht, Buket Öztekin, who contributed to making my workplace a nice place to be.

I would further like to thank the administrative and technical staff of Uppsala University for their support and professionalism, in particular Per Starbäck, Inga-Lill Holmberg, Jenny Rahbek and Ina Sörlid.


I am grateful to my friends, both in Lille and Uppsala. Thank you for staying by my side, even at times when I neglected you for the sake of my research.  

Last, but not least, without my dear family I would never have completed this work. Thank you! You should know that your support and encouragement was worth more than I can express in writing.
